Evaluating the Importance of Initial Conditions for Antarctic Sea Ice Seasonal Predictability with a Fully Coupled Model

### 2025-10-09 analysis/paper/access-ice.qmd
Adds acknowledgments and code + data (placeholder)

>>>>

# Acknowledgments

This work was supported by ARC SRIEAS Grant SR200100005 Securing Antarctica’s Environmental Future.

# Code and data availability

The underlying code for this study is available on github and can be accessed via this link https://github.com/eliocamp/access-s2_ice-eval.

Raw data of +S1 and +S2 forecast are not available due to size. 
Derived datasets required to reproduce the results are available in this zenodo repository: XXXXX

### 2025-10-09 analysis/paper/access-ice.tex
Adds acknowledgments and code + data (placeholder)

>>>>

\section{Acknowledgments}\label{acknowledgments}

This work was supported by ARC SRIEAS Grant SR200100005 Securing
Antarctica's Environmental Future.

\section{Code and data availability}\label{code-and-data-availability}

The underlying code for this study is available on github and can be
accessed via this link https://github.com/eliocamp/access-s2\_ice-eval.

Raw data of ACCESS-S1 and ACCESS-S2 forecast are not available due to
size. Derived datasets required to reproduce the results are available
in this zenodo repository: XXXXX
